\chapter{Basic Topology}

\setcounter{theorem}{11}
\begin{theorem}
	\label{theorem-2.12}
	Let $\left\lbrace E_n \right\rbrace$ for $n = 1, 2, 3, \ldots$ be a sequence of countable sets, and put
	\begin{equation}
	S = \bigcup_{n=1}^\infty E_n.
	\end{equation}
	Then $S$ is countable.
\end{theorem}

\begin{corollary}
	\label{theorem-2.12-corollary-1}
	Suppose $A$ is at most countable, and, for every $\alpha \in A$, $B_\alpha$ is at most countable. Put
	\begin{equation*}
	T = \bigcup_{\alpha \in A} B_\alpha.
	\end{equation*}
	Then $T$ is at most countable.
\end{corollary}

\begin{theorem}
	\label{theorem-2.13}
	\index{countable}
	Let $A$ be a countable set, and let $B_n$ be the set of all $n$-tuples $\left( a_1, \ldots, a_n \right)$, where $a_k \in A$ for $\left( k = 1, \ldots, n \right)$, and the elements $a_1, \ldots, a_n$ need not be distinct. Then $B_n$ is countable.
\end{theorem}

\setcounter{theorem}{18}
\begin{theorem}
	\label{theorem-2.19}
	Every neighborhood is an open set.
\end{theorem}

\begin{theorem}
	\label{theorem-2.20}
	If $p$ is a limit point of a set $E$, then every neighborhood of $p$ contains infinitely many points of $E$.
\end{theorem}

\setcounter{theorem}{22}
\begin{theorem}
	\label{theorem-2.23}
	A set $E$ is open if and only if its complement is closed.
\end{theorem}

\begin{corollary}
	\label{theorem-2.23-corollary-1}
	A set $F$ is closed if and only if its complement is open.
\end{corollary}

\setcounter{theorem}{27}
\begin{theorem}
	\label{theorem-2.28}
	Let $E$ be a nonempty set of real numbers which is bounded above. Let $y = \text{sup} E$. Then $y \in \overline{E}$. Hence $y \in E$ if $E$ is closed.
\end{theorem}

\setcounter{theorem}{30}
\begin{definition}
	\label{theorem-2.31}
	By an \textbf{\gls{open cover}} of a set $E$ in a metric space $X$ we mean a collection $\left\lbrace G_\alpha \right\rbrace$ of open subsets of $X$ such that $E \subset \cup_\alpha G_\alpha$.
\end{definition}

\begin{definition}
	A subset $K$ of a metric space $X$ is said to be \textbf{\gls{compact}} if every open cover of $K$ contains a \textit{finite} subcover.
\end{definition}

\setcounter{theorem}{34}
\begin{theorem}
	\label{theorem-2.35}
	Closed subsets of compact sets are compact.
\end{theorem}

\setcounter{theorem}{40}
\begin{theorem}
	\label{theorem-2.41}
	If a set in $\mathbb{R}^k$ has one of the following three properties, then it has the other two:
	\renewcommand{\labelenumi}{(\alph{enumi})}
	\begin{enumerate}
		\item $E$ is closed and bounded.
		\item $E$ is compact.
		\item Every infinite subset of $E$ has a limit point in $E$.
	\end{enumerate}
\end{theorem}

\setcounter{theorem}{46}
\begin{theorem}
	\label{theorem-2.47}
	A subset $E$ of the real line $\mathbb{R}^1$ is connected if and only if it has the following property: if $x \in E$, $y \in E$, and $x < z < y$, then $z \in E$.
\end{theorem}

\section{Exercises}
\input{chapters/chapter-2/exercises/exercise-1.tex}
\input{chapters/chapter-2/exercises/exercise-2.tex}
\input{chapters/chapter-2/exercises/exercise-3.tex}
\input{chapters/chapter-2/exercises/exercise-4.tex}

\input{chapters/chapter-2/exercises/exercise-12.tex}
\input{chapters/chapter-2/exercises/exercise-16.tex}
